### 2021-11-11 documentos/vector_space.tex
Comentarios sobre draft sección III.intro y III.A
Transpiled mainframe.

\subsection{A vector space of channels} % {{{
\cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
espacio. Quizá cuando haga falta se puede poner}
\par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{

@@

We can then see that all PCE quantum channels preserve $2^K$ components. In
fact, with the above picture, it is clearly revealed that the vector space has
dimension $2N$. Moreover, 
consider any subspace and chose the maximum number of linearly independent
elements (say $K$).  Any of the  $2^K$ subsets of those elements will yield a
unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
elements of the vector space. This means that any PCE quantum channel will preserve $2^K$ 
components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
\par

The dimension of the vector space $V$ of all multi-indices is $2N$, and we have
seen earlier that
\begin{equation}
W=\left\{
\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
\right\}
\label{eq:19}
\end{equation}
is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that
$W$ has $2^K$ elements. In other words, a vector $\vec\tau$ with the property
discussed above can only have $2^K$ elements equal to 1, for a given integer
$K$. \par

\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El
primero (simón, cambié de opinión)} \par

>>>>

\subsection{A vector space of channels} % {{{
\cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
espacio. Quizá cuando haga falta se puede poner}
\janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
parece una buena idea podría elaborar más cómo meterlo ahí}
\par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{

@@

% **********************************
% 
% We can show that all PCE quantum channels preserve $2^K$ components. 
% In
% fact, with the above picture, it is clearly revealed that the vector space has
% dimension $2N$. Moreover, 
% consider any subspace and chose the maximum number of linearly independent
% elements (say $K$).  Any of the  $2^K$ subsets of those elements will yield a
% unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
% elements of the vector space. This means that any PCE quantum channel will preserve $2^K$ 
% components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
% \par 
% 
% **********************************
% **********************************

We can show that all PCE quantum channels preserve $2^K$ components. 
First recall that a vector space of dimension $d$ over a field of $q$ elements
has $q^d$ elements~\cite{CitaAlgebraLineal}.
Now $V$ is a vector space on a field of two elements having dimension $2N$. 
% The dimension of the vector space $V$ of all multi-indices is $2N$, and 
We have
seen earlier that
\begin{equation}
W=\left\{
\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
\right\}
\label{eq:19}
\end{equation}
is a subspace of $V$. 
As such, $W$ has a given dimension $K$, which means that
$W$ has $2^K$ elements. In other words, a vector $\vec\tau$ with the property
discussed above can only have $2^K$ elements equal to 1, for a given integer
$K$. \par

% **********************************
% **********************************
% 
% \cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El
% primero (simón, cambié de opinión)} \par
